\documentclass[10pt]{beamer}

\usetheme{default}

\title{Writing Alectryon documents in LaTeX}

\usepackage{alectryon}
\usepackage{pygments}

\begin{document}
\maketitle

\begin{frame}[fragile]{Compiling this example}
  In LaTeX mode alectryon takes a LaTeX document as input, and produces a LaTeX
  document as output, with code blocks annotated:

  \begin{verbatim}
$ alectryon literate_LaTeX.tex
  # LaTeX → LaTeX,
    produces ‘literate_LaTeX.annotated.tex’
  \end{verbatim}
\end{frame}

\begin{frame}[fragile]{Showing input-output examples}
  In LaTeX Coq fragments are written as \verb|\begin{alectryon}{coq}{}|:

  \begin{alectryon}{coq}{}
  Goal exists x, x * x = 49 /\ x < 10.
    let rec t n :=
      (exists n; split; [reflexivity |]) || t (S n) in
    t 0.
    unfold lt.
    repeat constructor.
  Qed.
  \end{alectryon}
\end{frame}

\begin{frame}[fragile]{Customizing output}
  IO comments work as usual, but you can also put IO flags in the second argument of the \verb|{alectryon}| environment to specify the same flags that you would put on the first line of a \verb|.. coq::| directive.

  Note also that special characters in \verb|{alectryon}| environments don't need to be escaped, since Alectryon is used as a preprocessor.

  \begin{alectryon}{coq}{none}
  Require Import ZArith.
  \end{alectryon}

  \begin{alectryon}{coq}{unfold messages fails}
  Fail Check z + 0%nat.
  \end{alectryon}
\end{frame}

\begin{frame}{Help wanted!}
  We'd love to add support for converting between Coq and LaTeX, just like we have support for converting between Coq and reST.  Please send patches!
\end{frame}
\end{document}
